---
title: "WUP_04"
author: "Sabrina Andres"
date: "22 June 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

```{r}
gssdata=read_csv("GSScsv.csv")
```


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(gssdata,aes(x=DEGREE,y=WORDSUM))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The box for LT HIGH SCHOOL is different from that of JUNIOR COLLEGE and the box for GRADUATE. Because we can fit the entire LT HIGH SCHOOL box under those of COLLEGE and JUNIOR COLLEGE without touching, making the 50% for LT HIGH SCHOOL different to COLLEGE and JUNIOR COLLEGE.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=gssdata)
```

The means for BACHELOR, GRADUATE, and JUNIOR COLLEGE are closer to each other and do indicate that they are different from HIGH SCHOOL and LT HIGH SCHOOL. The three college levels above prove to be greater than those in the high school levels.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
model1 <- aov(WORDSUM~DEGREE,data=gssdata)
summary.aov(model1)
```
```{r}
plot(TukeyHSD(model1))
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 13.2, 2, 2))
plot(TukeyHSD(model1),las=2)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

I compared all degrees with the wordsum, checking for differences with the Gg_plots. I formed an opinion before confirming my opinion with favstats. I, then, confirmed the null hypothesis with the plots above.